\newglossaryentry{agile}{
  name={Agile},
  description={A set of software development methods based on iterative development, where requirements and solutions evolve.},
  plural=agiles
}

\newglossaryentry{Kanban}{
  name={Kanban},
  description={A method for managing tasks and workflows.},
  plural=Kanbans
}

\newglossaryentry{backlog}{
  name={Backlog},
  description={A list of tasks that need to be done.},
  plural=backlogs
}

 \newglossaryentry{Software stack}{
  name={Software stack},
  text={software stack},
  description={A set of software components that are used to build a software system.},
  plural=Software stacks
 }

 \newglossaryentry{Data flow}{
  name={Data flow},
  text={data flow},
  description={The flow of data between components in a system.},
  plural=Data flows
 }

 \newglossaryentry{functional requirements}{
  name={Functional requirements},
  text={Functional requirements},
  description={Requirements that define the functionality of a system.},
  plural=functional requirements
 }

\newglossaryentry{non-functional requirements}{
  name={non-functional requirements},
  text={non-functional requirements},
  description={Requirements that are not necessarily functional.},
  plural=non-functional requirements
}

\newglossaryentry{proprietary}{
  name={Proprietary},
  text={proprietary},
  description={A term used to describe software that is not open source and is owned by somebody.},
  plural=proprietary
}

\newglossaryentry{modular}{
  name={Modular},
  text={modular},
  description={Something that is made up of multiple parts that can be replaced or removed.},
  plural=modular
}

\newglossaryentry{sensors}{
  name={Sensors},
  text={sensors},
  description={A device that detects a physical phenomenon and converts it into a signal that can be read by a computer.},
  plural=sensors
}

\newglossaryentry{actuators}{
  name={Actuators},
  text={actuators},
  description={A device that converts a signal into a physical phenomenon.},
  plural=actuators
}

\newglossaryentry{4G}{
  name={4G},
  text={4G},
  description={A mobile communication standard that is used to transmit data over a cellular network.},
  plural=4G
}

\newglossaryentry{LTE-M}{
  name={LTE-M},
  text={LTE-M},
  description={A mobile communication standard that is used to transmit data over a cellular network.},
  plural=LTE-M
}

\newglossaryentry{ecosystem}{
  name={Ecosystem},
  text={ecosystem},
  description={Infermation technology specific definition: A set of components that work together to provide a specific functionality.},
  plural=ecosystems
}

\newglossaryentry{Open source}{
  name={Open source},
  text={open source},
  description={A term used to describe software that is free to use and modify.},
  plural=open source
}

\newglossaryentry{Apiary}{
  name={Apiary},
  text={apiary},
  description={A place where bees are kept.},
  plural=Apiary
}

\newglossaryentry{amplifier}{
  name={Amplifier},
  text={amplifier},
  description={A device that increases the power of a signal.},
  plural=amplifiers
}

\newglossaryentry{Brood chamber}{
  name={Brood chamber},
  text={brood chamber},
  description={A chamber in a beehive where the queen lays eggs.},
  plural=brood chambers
}

\newglossaryentry{GSM}{
  name={GSM},
  text={GSM},
  description={A mobile communication standard that is used to transmit data over a cellular network.},
  plural=GSM
}

\newglossaryentry{GPRS}{
  name={GPRS},
  text={GPRS},
  description={A mobile communication standard that is used to transmit data over a cellular network.},
  plural=GPRS
}

\newglossaryentry{SIM}{
  name={SIM},
  text={SIM},
  description={A SIM card (Subscriber Identity Module) is used to authenticate a user in a mobile network},
  plural=SIM
}

\newglossaryentry{DC}{
  name={DC},
  text={DC},
  description={Direct electrical current.},
  plural=DC
}

\newglossaryentry{Arduino IDE}{
  name={Arduino IDE},
  text={Arduino IDE},
  description={A development environment used to develop for the Arduino plattform.}
  plural={Arduino IDE}
}

\newglossaryentry{Sensor Block}{
  name={Sensor Block},
  text={Sensor Block},
  description={A closed system consisting of multiple sensors and/or actuators.},
  plural=Sensor Blocks
}

\newglossaryentry{Data Broker}{
  name={Data Broker},
  text={Data Broker},
  description={A service that manages the collection, storage, and distribution of data. MQTT in this context is a data broker.},
  plural=Data Brokers
}

\newglossaryentry{Backend}{
  name={Backend},
  text={Backend},
  description={The part of a system that is not directly accessible to the user.},
  plural=backends
}

\newglossaryentry{Database}{
  name={Database},
  text={Database},
  description={A system that stores data.},
  plural=databases
}

\newglossaryentry{User Interface}{
  name={User Interface},
  text={User Interface},
  description={The part of a system that is directly accessible to the user.},
  plural=User Interfaces
}

\newglossaryentry{Architecture}{
  name={Architecture},
  text={Architecture},
  description={The structure of a system.},
  plural=Architectures
}

\newglossaryentry{ESP32}{
  name={ESP32},
  text={ESP32},
  description={A microcontroller that is used to build IoT devices.},
  plural=ESP32
}

\newglossaryentry{Firmware}{
  name={Firmware},
  text={Firmware},
  description={The software that is installed on a microcontroller and generally doesn't get changed.},
  plural=Firmware
}

\newglossaryentry{Mosquitto}{
  name={Mosquitto},
  text={Mosquitto},
  description={A MQTT broker.},
  plural=Mosquitto
}

\newglossaryentry{MQTT}{
  name={MQTT},
  text={MQTT},
  description={A protocol that is used to communicate between devices.},
  plural=MQTT
}

\newglossaryentry{Prototype}{
  name={Prototype},
  text={Prototype},
  description={A working model of a system.},
  plural=Prototypes
}

\newglossaryentry{Docker}{
  name={Docker},
  text={Docker},
  description={A tool that is used to create and manage software containers.},
  plural=Docker
}

\newglossaryentry{TLS}{
  name={TLS},
  text={TLS},
  description={A protocol that is used to encrypt data.},
  plural=TLS
}

\newglossaryentry{HTTP}{
  name={HTTP},
  text={HTTP},
  description={A protocol that is used to transfer data over the internet.},
  plural=HTTP
}

\newglossaryentry{API}{
  name={API},
  text={API},
  description={An interface that is used to interact with a system.},
  plural=API
}

\newglossaryentry{Middleware}{
  name={Middleware},
  text={middleware},
  description={A software layer that is used to connect different systems.},
  plural=Middleware
}

\newglossaryentry{Endpoint}{
  name={Endpoint},
  text={endpoints},
  description={A point of interaction with a system.},
  plural=Endpoints
}

\newglossaryentry{ORM}{
  name={ORM},
  text={ORM},
  description={A system that is used to manage the relation between data in a database and the data in a programming language.},
  plural=ORM
}

\newglossaryentry{Reverse Proxy}{
  name={Reverse Proxy},
  text={reverse proxy},
  description={A system that is used to forward requests to a backend.},
  plural=Reverse Proxy
}

\newglossaryentry{Port}{
  name={Port},
  text={port},
  description={A number that is used to identify a specific service.},
  plural=Ports
}

\newglossaryentry{Timestamp}{
  name={Timestamp},
  text={timestamp},
  description={A number that is used to identify a specific point in time.},
  plural=Timestamps
}

\newglossaryentry{IOT}{
  name={IOT},
  text={IOT},
  description={The Internet of Things.},
  plural=IOT
}

\newglossaryentry{Off-Grid}{
  name={Off-Grid},
  text={off-grid},
  description={A system that is not connected to the electrical grid.},
  plural=Off-Grid
}

\newglossaryentry{Microcontroller}{
  name={Microcontroller},
  text={microcontroller},
  description={A small computer that is used to control devices.},
  plural=Microcontrollers
}

\newglossaryentry{CSV}{
  name={CSV},
  text={CSV},
  description={A file format that is used to store data.},
  plural=CSV
}

\newglossaryentry{Data sheet}{
  name={Data sheet},
  text={data sheet},
  description={A document that contains information about a specific component.},
  plural=Data sheets
}

\newglossaryentry{18650}{
  name={18650},
  text={18650},
  description={A common type of battery.},
  plural=18650
}

\newglossaryentry{Client}{
  name={Client},
  text={client},
  description={A user-facing system that is used to interact with a server.},
  plural=clients
}

\newglossaryentry{Proof of Concept}{
  name={Proof of Concept},
  text={proof of concept},
  description={A working model of a system that is used to demonstrate the feasibility of a system.},
  plural=Proof of Concepts
}

\newglossaryentry{Off the shelf}{
  name={Off the shelf},
  text={off the shelf},
  description={A system that is ready to use.},
  plural=Off the shelf
}